Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-07 sections/correlated-sicm-and-fm.tex
Added subsections (and some content to the first one)

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
Correlative SICM and FM, despite the mismatch in resolution, allows to gather
information which cannot be obtained by using a single technique
alone. However, the degree of correlation differs, depending on the FM
technique combined with SICM. Combining SICM and wide-field FM allows to image
the same region of the sample, which, for example, can be used to find a
region of interest such as an area containg synapses in a culture of a
neuronal network \cite{Novak2013,Scheenen2015}.

% Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
% (allerdings natürlich nicht innerhalb von irgendetwas). Und irgendwie ist
% das ja auch nicht der "Haupt"-Vorteil, sondern, dass man überhaupt
% Fluoreszenz sehen kann.

@@

@@

Another very delicate sample, because of their three-dimensional, upright (?) structure are cilia.
Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
distinguish between surface and sub-surface cilia, which could not be detected with SICM 
\cite{Zhou2018}.

>>>>

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:

% Assume a figure here which shows the different degrees of correlation
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+fm}
  \caption{%
    \textbf{Combining SICM and wide-field fluorescence microscopy.}
    \textbf{a:}
    \textbf{b:} FM image of presynaptic nerve terminals stained with
    FM1-43. \textbf{c:} Overlay of the FM-image and two SICM recordings of the
    same region. \textbf{d:} 3D-representation of the SICM recordings.
    \textbf{b--d:} Reprinted with permission from ref \cite{Scheenen2015}.
  }
  \label{fig:sicm+fm}
\end{figure}

Correlative SICM and FM, despite the mismatch in resolution, allows to gather
information which cannot be obtained by using a single technique
alone. However, the degree of correlation as well as the technical
implementation differs, depending on the FM
technique combined with SICM.

\subsection{Combining SICM and wide-field FM}
\label{sec:SICM+widefield}
Combining SICM and wide-field FM allows to image the same region of
the sample with both techniques (Fig.~\ref{fig:sicm+fm}a). Technically, this
combination is simple, since most implementations of SICM are built on
inverted optical microscopes. However, due to the
poor $z$-resolution of wide-field FM, a direct correlation of data from the
along the optical axis, $z$, which, for example, can be used to find a region
of interest such as an area containing synapses in a culture of a neuronal
network \cite{Novak2013,Scheenen2015}
(Fig.~\ref{fig:scheenen2015}). Furthermore, a combination of wide-field FM and
SICM has been used to first identify primary cilia in a cell culture and
subsequently use SICM to reveal whether the selected cilium was extending into
the extracellular space or was embedded in the cell, an information which
could not be retrieved by using FM alone \cite{Zhou2018}.
% Den folgenden Teil verstehe ich nicht wirklich, SICM kann ja auch 3D
% (allerdings natürlich nicht innerhalb von irgendetwas). Und irgendwie ist
% das ja auch nicht der "Haupt"-Vorteil, sondern, dass man überhaupt
% Fluoreszenz sehen kann.

@@

% Another very delicate sample, because of their three-dimensional, upright structure are cilia.
% Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
% distinguish between surface and sub-surface cilia, which could not be detected with SICM 
% \cite{Zhou2018}.
\subsection{Combining SICM and confocal FM}

\subsection{Surface scanning}

@@
